Base Model

### 2022-04-22 modeling/base-models.Rmd
close #26

library(tidyverse)
library(lme4)
library(boxr)
box_auth()
```

@@

```{r}
data <- box_read("947772227392") %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

@@

```{r}
resnull <- glmer(justicevot ~ (1|id)+1 ,family = "binomial", data = data)  
summary(resnull)
```
We are good to proceed

@@

# Base Model

@@

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
summary(mod1)
```

>>>>

library(tidyverse)
library(lme4)
library(boxr)
box_auth()

# data id
amicus_only <- "948366662469"
full_cases <- "948832669583"

#**Note: The data used in these models is *the full set* of abortion cases. Cases *without* amici are included and their frame measures are all 0s.**
```

@@

```{r}
data <- box_read(amicus_only) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         cirsplit = as.factor(cirsplit),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

@@

```{r}
resnull <- glmer(justicevot ~ (1|id)+1 ,family = "binomial", data = data)  
summary(resnull)
```
ICC for model with no covariates

@@

# Base Model (lcdisdirfem)

@@

```{r}
base_mod <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
summary(base_mod)
```

ICC for base model

```{r}
calc_ICC(base_mod)
```

# Base Model 2 (cirsplit)

Use cirsplit instead of lcdisdirfem

```{r}
base_mod_2 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + cirsplit,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
summary(base_mod_2)
```

ICC for base model

```{r}
calc_ICC(base_mod_2)
```
